---
title: "Tusket 2022 Counts Summary"
output: pdf_document
date: '2022-08-05'
author: Mark Billard, DFO-Science
---
```{r setup, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
```

```{r message=FALSE, results=FALSE, warning=FALSE}
##Make sure you have run the below script to get the output objects needed for this document
source("~/git/ALOSA.functions/Assessment_Script_Tusket_2022.R")
```

This document summarizes the daily counts of Gaspereau, a collective name for Alewife and Blueback Herring, at three fish ladders in the Tusket River, Nova Scotia in the spring of 2022. The vast majority of spawning habitat for Alewife and Blueback Herring is upstream of the Lake Vaughan and the Powerhouse fish ladders, which both provide access to Lake Vaughan. The Carleton fish ladder, located at the north end of Lake Vaughan, allows fish to access the Carleton branch of the watershed above the Carleton Dam. Fish that exit the Lake Vaughan or Powerhouse ladder can also access the Quinan/Tusket branch of the watershed up to the Great Barren Lake Dam.

The counts from the Lake Vaughan fish ladder are used to assess the Alewife population relative to reference points. Counts at the Lake Vaughan ladder are also used to assess the Blueback Herring population. Counts from the Powerhouse fish ladder were relatively low compared to the Lake Vaughan fish ladder and were not included in the assessment to allow for representative comparisons with assessment data from previous years where counts at the Powerhouse fish ladder were not conducted, and because the low number of Gaspereau migrating through the Powerhouse ladder would not significantly change the status of the stock. Counts from the Powerhouse ladder were not conducted in recent years, as it was thought that Gaspereau primarily migrated through the Lake Vaughan fish ladder.

Counts were completed following a two-way stratified random sampling design. Each day, a total of 24 five minute video blocks were counted. To ensure that different parts of the day were represented, each day was broken into six sections, or strata, and four five minute video counts were sampled from each strata. Dividing the day into sections, or strata, is important for providing an accurate estimate of the number of fish migrating upstream through the fish ladders, as there are times of the day when more fish migrate than during other times of the day. 

The four video counts from each stratum (section) were averaged, and that average was multiplied by the number of five minute blocks within each stratum of the day. For example, Strata 2 is from 0500 to 1030, so contains 69 five minute blocks. If the average count in Strata 2 for a given day was 20, we multiply 20 by 69 to give us a total of 1380 fish for Strata 2. We repeat this for each stratum in a day, and sum all strata totals to get the daily totals.

A more in depth description of this assessment method is described by Bowlby and Gibson in the CSAS document "River Herring Assessment for the Tusket River, Nova Scotia" under the "Escapement" section.

\newpage
Lake Vaughan Fish Ladder Counts

Counts were conducted from April 1 2022 to June 21 2022 at the Lake Vaughan fish ladder (Fig. 1). Counts stopped when the daily total was below 1000 for three days in a row. A total of 1,662,007 +/- 51,040 Alewife, and 8,463 +/- 1,196 Blueback Herring were estimated to have ascended the ladder. 
```{r}
plot(daily.summary.A$dayofyear,daily.summary.A$total,type="l",xaxt="n",yaxt="n",xlab="Date",ylab="Thousands of Fish",col="red")
axis(1,at=c(90,105,121,135,152,167),labels=c("April 1","April 15","May 01","May 15","June 01","June 15"))
axis(2,at=c(0,10000,20000,30000,40000,50000,60000,70000,80000,90000),labels=c(0,10,20,30,40,50,60,70,80,90))
lines(daily.summary.B$dayofyear,daily.summary.B$total,col="blue")
```

Figure 1. Lake Vaughan Fish Ladder Counts for the Tusket River, 2022. The red line is for daily counts of Alewife, and the blue line is for daily counts of Blueback Herring. 

\newpage
Carleton Fish Ladder Counts

Counts were conducted from April 14 2022 to June 8 2022 at the Carleton/Raynardton fish ladder (Fig. 2). A lack of species sampling prevented an estimate of the number of Alewife and Blueback Herring, so all counts refer to the collective gaspereau. A number of factors described below prevented the entire migration from being enumerated.

A camera outage resulted in no counts completed for May 7th. Some of May 6th and May 8th were also lost, but enough was counted that the missing strata were estimated with a linear model to fill in missing counts.

Counts could not be completed from May 24th to May 26th. Large numbers of fish were counted moving down through the ladder, and schools of fish were observed milling at the top of the ladder, in Raynardton Lake. It is possible that these fish were post spawning, downstream migrants. Since downstream migrants would have been counted migrating upstream and would contribute to the total escapement of the ladder, counting them as a "negative" moving downstream would be inappropriate, and inaccurately represent the total migration. 

Downstream migration behaviour occurred on June 1st, and persisted until the camera was removed on June 8th. None of those counts are representative of upstream migration, so only counts completed where no downstream migration occurred are presented here.

```{r}
plot(carleton.summary$dayofyear,carleton.summary$total,type="l",xaxt="n",yaxt="n",xlab="Date",ylab="Thousands of Fish")
rect(126,0,128,max(carleton.summary$total,na.rm=T),col="gray")
rect(143,0,147,max(carleton.summary$total,na.rm=T),col="gray")
axis(1,at=c(105,121,135,152),labels=c("April 15","May 01","May 15","June 01"))
axis(2,at=c(0,5000,10000,15000,20000,25000,30000),labels=c(0,5,10,15,20,25,30))
```

Figure 2. Carleton Fish Ladder counts for the Tusket River, 2022. The leftmost grey rectangle covers the time period where there was a camera outage and no counts were completed. The right most grey rectangle covers the time period where downstream migration was occurring and accurate counts of fish leaving the ladder could not be completed. Alewife and Blueback Herring were not differentiated for the counts presented in this figure.

\newpage
Powerhouse Fish Ladder Counts

Counts were conducted from May 2 2022 to June 15 2022 at the Powerhouse fish ladder (Fig. 3). A lack of species sampling prevented an estimate of the number of Alewife and Blueback Herring, so all counts refer to the collective gaspereau. Downstream migration from June 6th to June 7th prevented accurate counts. The camera was removed due to ladder modifications by NSP midday June 7th, and was re-installed midday June 10th. Counts were also done from June 15th to June 20th (not shown), but were all 0. Note that the scale for the below figure is numbers of fish, rather than thousands of fish as in the previous figures.

```{r}
plot(powerhouse.summary$dayofyear,powerhouse.summary$total,type="l",xaxt="n",yaxt="n",xlab="Date",ylab="Number of Fish")
rect(156,0,161,max(powerhouse.summary$total,na.rm=T),col="gray")
axis(1,at=c(121,135,152,167),labels=c("May 01","May 15","June 01","June 15"))
axis(2,at=c(0,500,1000,1500),labels=c(0,500,1000,1500))
# lines(powerhouse.summary$dayofyear,powerhouse.summary$clow,col="red",lty=3)
# lines(powerhouse.summary$dayofyear,powerhouse.summary$chigh,col="red",lty=3)
```

Figure 3. Powerhouse Fish Ladder counts for the Tusket River, 2022. The grey rectangle covers the time period where downstream migration was observed, and the camera was removed from the ladder due to modifications to the fish ladder by NSP. Alewife and Blueback Herring were not differentiated for the counts presented in this figure.


\newpage
Overlaying the counts from the three ladders demonstrates the different numbers of fish that passed through each fish ladder (Fig. 4). 

```{r}
plot(daily.summary.A$dayofyear,daily.summary.A$total,type="l",xaxt="n",yaxt="n",xlab="Date",ylab="Thousands of Fish",col="red")
axis(1,at=c(90,105,121,135,152,167),labels=c("April 1","April 15","May 01","May 15","June 01","June 15"))
axis(2,at=c(0,10000,20000,30000,40000,50000,60000,70000,80000,90000),labels=c(0,10,20,30,40,50,60,70,80,90))
lines(daily.summary.B$dayofyear,daily.summary.B$total,col="blue")
lines(carleton.summary$dayofyear,carleton.summary$total)
lines(powerhouse.summary$dayofyear,powerhouse.summary$total,col="green")
```

Figure 4. Daily counts from the Lake Vaughan Fish Ladder, Carleton Fish Ladder, and Powerhouse fish Ladder on the Tusket River, Nova Scotia, in Spring of 2022. The red line represents daily Alewife counts from the Lake Vaughan Fish Ladder, the blue line represents daily Blueback Herring counts from the Lake Vaughan Fish Ladder, the black line represents daily Gaspereau counts from the Carleton Fish Ladder, and the green line represents daily counts from the Powerhouse Fish Ladder.

\newpage
Appendix

```{r table}
daily.summary.A.out<-daily.summary.A
names(daily.summary.A.out)<-c("Month", "Day", "Day of Year", "Total", "Standard Deviation", "clow", "chigh")
kable(daily.summary.A.out[,1:5],caption="Daily count estimates of Alewife leaving the Lake Vaughan Fish Ladder. Counts are presented for April (Month = 4), May (Month = 5), and June (Month = 6). Total is the total number of Alewife estimated to have exited the ladder that day, and Standard Deviation is the standard deviation for that daily total estimate.")

daily.summary.B.out<-daily.summary.B
names(daily.summary.B.out)<-c("Month", "Day", "Day of Year", "Total", "Standard Deviation", "clow", "chigh")
kable(daily.summary.B.out[,1:5],caption="Daily count estimates of Blueback Herring leaving the Lake Vaughan Fish Ladder. Counts are presented for May (Month = 5) and June (Month = 6). Total is the total number of Blueback Herring estimated to have exited the ladder that day, and Standard Deviation is the standard deviation for that daily total estimate.")

carleton.summary.out<-carleton.summary
names(carleton.summary.out)<-c("Month", "Day", "Day of Year", "Total", "Standard Deviation", "clow", "chigh")
kable(carleton.summary.out[,1:5],caption="Daily count estimates of Gaspereau leaving the Carleton Fish Ladder. Counts are presented for April (Month = 4) and May (Month = 5). Total is the total number of Gaspereau estimated to have exited the ladder that day, and Standard Deviation is the standard deviation for that daily total estimate.")

powerhouse.summary.out<-powerhouse.summary
names(powerhouse.summary.out)<-c( "Month", "Day", "Day of Year", "Total", "Standard Deviation", "clow", "chigh")
kable(powerhouse.summary.out[,1:5],caption="Daily count estimates of Gaspereau leaving the Powerhouse Fish Ladder. Counts are presented for April (Month = 4) and May (Month = 5). Total is the total number of Gaspereau estimated to have exited the ladder that day, and Standard Deviation is the standard deviation for that daily total estimate. Note that counts are for Alewife and Blueback Herring combined, as no species ID were completed at the ladder.")
```
